---
title: "PSY 8960 Week 12"
author: "Annie Griebie"
date: "`r Sys.Date()`"
output: html_document
---

## Script Settings and Resources
```{r script_settings_and_resources}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(doParallel)
library(wordcloud)
library(tm)
library(tidytext)
library(ldatuning)
library(topicmodels)
library(textstem)
library(RedditExtractoR)
library(qdap)
library(RWeka)
```

## Data Import and Cleaning
#reading in reddit data using RedditExtractoR which allows you to search for subreddit (IOPsychology). Added sort by "new" because that will make sure within the last year rather than selecting "hot"
```{r data_import_and_cleaning}
# foundthreads <- find_thread_urls(
  subreddit = "IOPsychology",
  sort_by = "new",
  period = "year"
)

# urls_content <-get_thread_content(foundthreads$url)

# title <- urls_content$threads$title
# upvotes <- urls_content$threads$upvotes
#creating tibble with title and upvotes
# week12_tbl <- tibble(title, upvotes)
#adding code to save data files instead of downloading again 
# write_csv(week12_tbl, file = "../data/week12.csv")
```

```{r data_import_and_cleaning}
week12_tbl <- read.csv("../data/week12.csv")
```
  
#NLP - preprocessing # come back because need to install java
```{r NLP_preprocessing}
#Creating io_corpus_original
io_corpus_original <- VCorpus(VectorSource(week12_tbl$title))
```

```{r NLP_preprocessing}
#Creating new lemmatized pre-processed corpus
io_corpus <- io_corpus_original %>%
#removing dashes 
tm_map(content_transformer(str_replace_all), pattern = "-|/", replacement = "")%>%
#removing abbreviations
tm_map(content_transformer(replace_abbreviation))%>%
#removing contractions
tm_map(content_transformer(replace_contraction))%>%
#removing 
tm_map(content_transformer(str_to_lower))%>%
#removing numbers
tm_map(removeNumbers) %>%
#removing punctuation
tm_map(removePunctuation) %>%
#removing white space
tm_map(stripWhitespace) %>%
tm_map(stemDocument, language = "english") %>%
#removing words with IO psychology, did not remove words specifically referring to "pscyhology" or "psych" because directions only mentioned to remove referenes to IO psychology and variaitons of the term, I thought including "psychology" and variations of that term was not the same and could also prove beneficial for sorting topics that might mention connections from IO to other subfields of psychology specifically for individuals who might have a background in Quantitative Psychology that might be looking to find a career or learn more about IO psychology specifically.
tm_map(removeWords, c(stopwords("en"), "io psychology", "i o psychology", "iopsychology", "io", "i o", "riopsychology"))
```      

#creating function compare_them
```{r}
compare_them <- function (corpus1, corpus2) {
  row <- sample(1:length(corpus1),1)
  output <- list(corpus1[[row]]$content, corpus2[[row]]$content)
  return(output)
}

compare_them(io_corpus_original, io_corpus)
```

##Analysis

#creating Bigram DTM following week 12 powerpoint and io_slim dtm
```{r Bigram DTM}
myTokenizer <- function(x) {
  NGramTokenizer(x,
Weka_control(min=1, max=2))}
io_dtm <-DocumentTermMatrix(io_corpus,
control = list(
tokenize = myTokenizer
))
io_slim_dtm <- removeSparseTerms(io_dtm, 0.996)
```

#Tuning an LDA model (topic extraction)
#will not run, R session terminates with a fatal error when including "Griffiths2004" model so removed in order to complete assignment questions
```{r lda}
local_cluster <- makeCluster(7)
registerDoParallel(local_cluster)
tuning<- FindTopicsNumber(
  io_dtm,
  topics = seq(2, 15, 1),
  metrics = c(
              "CaoJuan2009",
              "Arun2010",
              "Deveaud2014"),
  control = list(seed = 424),
  verbose =T
)
FindTopicsNumber_plot(tuning)
stopCluster(local_cluster)
registerDoSEQ
```
## This is the correct LDA model with the "Griffiths2004" metric included, only included as a comment because with it included will create fatal error in R session. 
#{r lda}
local_cluster <- makeCluster(7)
registerDoParallel(local_cluster)
tuning<- FindTopicsNumber(
  io_dtm,
  topics = seq(2, 15, 1),
  metrics = c("Griffiths2004",
              "CaoJuan2009",
              "Arun2010",
              "Deveaud2014"),
  control = list(seed = 424),
  verbose =T
)
FindTopicsNumber_plot(tuning)
stopCluster(local_cluster)
registerDoSEQ
#The link below is the stack overflow page I consulted to try to find a way to make the ldatuning package run with the "Griffiths2004" metric on my Mac system. I followed all directions but was still unable to run the code witout removing the "Griffiths2004" metric, UMN IT services suggeseted it was a personal device system error. 
https://stackoverflow.com/questions/67480220/fatal-error-in-r-on-mac-when-using-ldatuning-package

#LDA betas with 3 topics. Chose to set topics to 3 because with higher values, even 5, the topics seemed to get more jumbled and confused with less clear distinction. 
```{r}
lda_results <- LDA(io_dtm, 3)

lda_betas <-tidy(lda_results, matrix="beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  arrange(topic, -beta)
```

#LDA gammas
```{r}
lda_gammas <- tidy(lda_results, matrix= "gamma") %>%
  group_by(document) %>%
  top_n(1, gamma) %>%
  slice(1) %>%
  ungroup %>%
  rename(doc_id = document, probability = gamma) %>%
  arrange(doc_id) %>%
  mutate(doc_id = as.numeric(doc_id))
```

#Creating topics tbl
```{r}
doc_id <-c(1:nrow(week12_tbl))
original <- week12_tbl$title
original_tbl <- tibble(doc_id, original)
topics_tbl <- original_tbl %>%
  left_join(lda_gammas, by = "doc_id"
) %>%
  select(doc_id, original, topic, probability)
```
#Question1: What topics do the final topic lists map onto based on the beta matrix
#Answer 1:
#1 topic 1 seems to be capturing posts discussing work within IO psychology. 
#2. topic 2 seems to be capturing posts discussing careers in IO pschology.
#3. topic 3 seems to be capturing posts discussing psychology as a whole.


#Question2: Look at the orginal text of documents with the highest and lowest probabilities assigned to each document. Do your topic names derived from your interpretation of the beta matrix conceptually match with the content of the original posts? What kind of validity evidence does your answer to this question represent?
#Answer 2: The topic names derived from my interpretation of hte beta matrix seem to loosely conceptually match with the content of the original posts, though there is not a perfect match. I think the kind of validity evidence my answer to this question represents is content validity. Namely the topics are each a grouping of a construct the content of which is determined by the content of the word contained in the title of the post. Additionally, because some of the topics do overlap this question also relates to construct validity, because with overlap between topics there is construct contamination thus suggesting a lack of construct validity. 



#create final_tbl dataset containing the contents of topics_tbl plus upvote count and add statistical test
```{r}
final_tbl <- topics_tbl %>%
  mutate(upvotes = week12_tbl$upvotes)
```

#Statistical analysis to determine if upvotes differs by topic
```{r}
upvotes_topic <-aov(upvotes ~ topic, final_tbl)
summary(upvotes_topic)
```
#The results of this anova suggest that there was not a significant difference between the group mean number of upvotes across topics (p>0.05).

##Visualization
#creating a wordcloud of io_dtm 
```{r visualization_wordcloud}
iowordcloud_tbl <- as_tibble(as.matrix(io_dtm))
wordcounts <-colSums(iowordcloud_tbl)
wordnames <- names(iowordcloud_tbl)
wordcloud(wordnames, wordcounts, max.words = 20, scale = c(2, 0.25))
```
#The wordcloud seems to suggest that the most used used words include work, research and job. These are expected results considering the topic lists generated as well as the overall state of the field of IO psychology, many people are interested in finding work within the field of IO and research is an important part of many of the different jobs and activities of IO psychologists. Additionally, the topic of "psycholog" which seems to be a variation of psychology is one of biggest topics. This makes sense as this is a set of reddit posts for IO psychologists. As indicated earlier in document I did not remove variations of the word psychology because it was not specifically a reference to "IO psychology" as suggested in the directions. 